Robustly decorrelating errors with mixed quantum gates

### 2019-08-27 decorrelation/mixed_unitaries.tex
one more small change

In this case, if (\ref{eq:minimization}) is satisfied, the resulting error channel will be \textit{exactly} a Pauli Channel. If this is achievable, then the circuit can be more efficiently simulated by Monte Carlo methods. Better yet, if the circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} Other authors have considered the problem of finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013, Puzzuoli2014} but, unlike our routine, this does not produce a channel that is decomposable into a given family of controls.

>>>>

In this case, if (\ref{eq:minimization}) is satisfied, the resulting error channel will be \textit{exactly} a Pauli Channel. If this is achievable, then the circuit can be more efficiently simulated by Monte Carlo methods. Better yet, if the bare circuit consists of only Clifford gates, stabilizer methods can be used in conjunction with the Monte Carlo methods to give sub-exponential simulation times.\cite{quant-ph/9807006} Other authors have considered the problem of finding the closest Pauli or Clifford Channel to a given process \cite{Magesan2013, Puzzuoli2014} but, unlike our routine, this does not produce a channel that is decomposable into a given family of controls.
